Code Clones: To refactor or not to refactor?

### 2020-05-08 ase/paper.tex
Updates from Overleaf

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate several maintainability metrics (duplication, complexity, unit size, code volume) to determine whether it improves the code. This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.

>>>>

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level. This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.
